\chapter{Model Validation}
\label{chp:MV}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Physical replicas of selected units are constructed and inflated. The deformation is observed and compared with the modelled behaviour as calculated by the FEM software.

\section{Mixing and Casting}

The modular mould as described in Section~\ref{ssec:pc} is assembled according to the desired unit layout. Mold Star 15 is mixed and cast as per Section~\ref{ssec:mac}. After the cure time has passed the unit is removed from the mould and excess material is carefully cut off. Figure~ shows a filled mould.

\section{Experimental Setup}

The experimental setup as described in Section~\ref{ssec:pc} is constructed. Figure~ shows the experimental setup with no unit in place. A sealant is used to prevent air leakage at the point of entry of the pressure supply tube.

\section{Results}

Three units were selected for model validation.

\subsection{Unit 1}

The first unit selected is grid\_ as illustrated in Figure~. This unit was selected as a random control unit. This unit does not perform well according to any specific unit deformation case. This unit has complex internal geometry that may deform in unusual ways. Cavities exist which are potentially inaccessible from the undeformed state, but become accessible as the unit inflates.

\subsection{Unit 2}

The second unit selected is grid\_ as illustrated in Figure~. This unit was selected as a linearly extending unit. This unit performs well according to the uniaxial deformation case. Cavities exist which are potentially inaccessible from the undeformed state, but become accessible as the unit inflates.

\subsection{Unit 3}

The third unit selected is grid\_ as illustrated in Figure~. This unit was selected as a linearly extending unit. This unit performs well according to the uniaxial deformation case when surrounded by identical units, but performs poorly when on its own.

\section{Issues Encountered}

Issues were encountered during model validation. Some were attempted to account for beforehand and some were unforeseen.

Mould cells were not manufactured exactly to tolerances.